ASYMPTOTIC VALIDITY OF A FULLY SEQUENTIAL ELIMINATION PROCEDURE FOR INDIFFERENCE-ZONE RANKING AND SELECTION WITH TIGHT BOUNDS ON PROBABILITY OF CORRECT SELECTION

### 2015-05-04 paper/wish/wsc15paper.tex
conference

%% LyX 2.1.2.1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[11pt,english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\geometry{verbose,tmargin=1.5cm,bmargin=1.5cm,lmargin=1.5cm,rmargin=1.5cm}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\onehalfspacing

\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
%\documentclass[opre,blindrev]{informs3} % current default for manuscript submission

% current default line spacing
%%\OneAndAHalfSpacedXII 
%%\DoubleSpacedXII
%%\DoubleSpacedXI

% If hyperref is used, dvi-to-ps driver of choice must be declared as
%   an additional option to the \documentclass. For example
%\documentclass[dvips,opre]{informs3}      % if dvips is used 
%\documentclass[dvipsone,opre]{informs3}   % if dvipsone is used, etc.

%%% OPRE uses endnotes
\usepackage{endnotes}
\let\footnote=\endnote
\let\enotesize=\normalsize
\def\notesname{Endnotes}%
\def\makeenmark{\hbox to1.275em{\theenmark.\enskip\hss}}
\def\enoteformat{\rightskip0pt\leftskip0pt\parindent=1.275em
  \leavevmode\llap{\makeenmark}}

\date{}

@@

\usepackage{algorithm,algorithmic,enumerate}

%% Setup of theorem styles. Outcomment only one. 
%% Preferred default is the first option.
  % Preferred (Theorem 1, Lemma 1, Theorem 2)
%\TheoremsNumberedByChapter  % (Theorem 1.1, Lema 1.1, Theorem 1.2)

\makeatother

\usepackage{babel}
\begin{document}

\title{Asymptotic Validity of a Fully Sequential Elimination Procedure for
Indifference-Zone Ranking and Selection with Tight Bounds on Probability
of Correct Selection}

\author{Saul Toscano\\
{\small{}School of Operations Research and Information Engineering,
Cornell University}\\
Peter I. Frazier\\
{\small{}School of Operations Research and Information Engineering,
Cornell University}}

\maketitle
We consider the indifference-zone (IZ) formulation of the ranking
and selection problem. Conservatism leads classical IZ procedures
to take too many samples in problems with many alternatives. The Bayes-inspired
Indifference Zone (BIZ) procedure, proposed in Frazier (2014), is
less conservative than previous procedures, but its proof of validity
requires strong assumptions. In this paper, we present a new proof
of asymptotic validity that relaxes these assumptions.

\section{Introduction}

One common problem in simulation is that of choosing the best among
several simulated systems. The problem of deciding how many samples
to use from each alternative to support our selection as the best
is the ranking and selection problem. An efficient solution to this
problem has to balance between the time spent simulating and the quality
of the selection.

This paper will consider the indifference-zone (IZ) formulation of
the ranking and selection problem, in which we choose the best system
with probability larger than a pre-specified threshold, whenever the
distance between the best system and the others is sufficiently large.
We say that a sampling procedure having this property satisfies the
IZ guarantee and the set of system configurations under which the
best alternative is better than the second best by at least some given
$\delta>0$ is called the preference zone (PZ). The seminal work dates
back to Bechhofer (1954), with early work compiled in the monograph
Bechhofer et al. (1968). The progress in the area has been summarized
in Bechhofer et al. (1995), Swisher et al. (2003), Kim and Nelson
(2006, 2007) and Frazier (2014).

The goal of an IZ algorithm is to take as few samples as possible
while the IZ guarantee is satisfied. The first IZ procedures presented
in Bechhofer (1954), Paulson (1964), Fabian (1974), Rinott (1978),
Hartmann (1988, 1991), Paulson (1994) satisfy the IZ guarantee, but
they usually take too many samples when there are many alternatives,
in part because their probability of correct selection (PCS) is much
larger than the probability specified by the user. A reason of this
is the use of the Bonferroni's inequality which leads to sample more
than necessary. More recent algorithms in Kim and Nelson (2001), Goldsman
et al. (2002), Hong (2006) improve the performance but they still
use the Bonferroni's inequality, and so the methods are inefficient
when there are several systems. Procedures in Kim and Dieker (2011),
Dieker and Kim (2012) do not use the Bonferroni's inequality only
when compare groups of three alternatives.

Since the classic IZ procedures take too many samples with many alternatives,
these methods are unpopular when there are more than a few hundred
alternatives. However, Frazier (2014) presented a new sequential elimination
IZ procedure, called BIZ (Bayes-inspired Indifference Zone), whose
lower bound on worst-case probability of correct selection in the
preference zone is tight in continuous time, and almost tight in the
discrete time. In numerical experiments, the number of samples required
by BIZ is significantly smaller than that of the most popular IZ procedures,
especially on problems with many alternatives. Unfortunately, the
proof that the BIZ procedure satisfies the IZ guarantee for the discrete-time
case assumes that variances are known and have an integer multiple
structure which is not very realistic. In practice, variances are
unknown. However, asymptotically we can use a central limit theorem
that allows us to prove the asymptotic validity of the BIZ procedure
for the discrete-time case. Moreover, we only need to assume that
the systems are independent, identically distributed and have finite
variance.

Kim et al. (2006) also proves the asymptotical validity of a IZ procedure.
Our proof is larger because the BIZ procedure is more sophisticated
and the bound for the PCS is tighter. To prove the case when the variances
are known, we use a theorem for Ergodic processes that shows how to
standardize the output data to make them behave like Brownian motion
processes in the limit. We also use an extension of the Continuous
Mapping Theorem (Theorem 5.5 of Billingsley 1968) to see that the
algorithm behaves like a sequential elimination IZ procedure with
a Brownian motion process instead of the standardized sum of the output
data in the limit, and then we use the results of the paper of Frazier
\cite{key-5} to prove the validity of this algorithm in the limit.
Finally, we use a random change of time argument to prove the case
when the variances are unknown.

This paper is organized as follows: In $\text{§}2$, we recall the
indifference-zone ranking and selection problem. In $\text{§}3$,
we recall the Bayes-inspired IZ (BIZ) procedure. In $\text{§}4$,
we present the proof of the validity of the algorithm when the variances
are known. In $\text{§}5$, we prove the case when the variances are
unknown. In $\text{§}6$, we present some simulations showing the
effectiveness of the algorithm. In $\text{§}7$, we conclude.

\section{Indifference-Zone Ranking and Selection }

Ranking and Selection is a procedure for selecting the best system
among a finite set of alternatives, i.e. the system with the largest
mean. The method selects a system as the best based on the samples
that are observed sequentially over the time. If the best system is
selected, we say that the procedure has made the \emph{correct selection}
(CS). We define the \emph{probability of correct selection} as 
\[
\mbox{PCS}\left(\mu,\lambda\right)=\mathbb{P}_{\mu,\lambda}\left(\hat{x}\in\mbox{arg max}_{x}\mu_{x}\right)
\]
where $\hat{x}$ is the alternative chosen by the procedure and $\mathbb{P}_{\mu,\lambda}$
is the probability measure under which samples from system $x$ have
mean $\mu_{x}$ and finite variance $\lambda_{x}^{2}$.

In the Indifference-Zone Ranking and Selection, the procedure is indifferent
in the selection of a system whenever the means of the populations
are nearly the same. Formally, let $\mu=\left[\mu_{k},\ldots,\mu_{1}\right]$
be the vector of the true means, the \emph{indifference zone} is defined
as the set $\left\{ \mu\in\mathbb{R}^{k}:\mu_{\left[k\right]}-\mu_{\left[k-1\right]}<\delta\right\} $.
The complement of the indifference zone is called the \emph{preference
zone} (PZ) and $\delta>0$ is called the indifference zone parameter.
We say that a procedure meets the \emph{indifference-zone (IZ) guarantee
}at $P^{*}\in\left(1/k,1\right)$ and $\delta>0$ if
\[
\mbox{PCS}\left(\mu,\lambda\right)\geq P^{*}\mbox{ for all }\mu\in\mbox{PZ}\left(\delta\right).
\]
We assume $P^{*}>1/k$ because IZ guarantees can be meet by choosing
$\hat{x}$ uniformly at random from among $\left\{ 1,\ldots,k\right\} $.

\section{The Bayes-inspired IZ (BIZ) Procedure}

BIZ is an elimination procedure. This procedure maintains a set of
alternatives that are in contention, and it takes samples from each
alternative in this set at each point in time. At beginning, all alternatives
are in contention, and over the time alternatives are eliminated.
The procedure ends when there is only one alternative in the contention
set and this remain alternative is chosen as the best.

Frazier (2014) showed that the BIZ procedure with known common variance
satisfies the IZ guarantee when the systems follow the normal distribution
, with tight bounds on worst-case preference-zone in continuous time.
He also proved that this procedure retains the IZ guarantee when the
systems follow the normal distribution, and the variances are known
and are integer multiples of a common value. The continuous time version
of this procedure also satisfies the IZ guarantee, with a tight worst-case
preference-zone PCS bound.

The discrete-time BIZ procedure for unknown and/or heterogeneous sampling
variances is given in Alg. 2. It takes a variable number of samples
from each alternative, and $n_{tx}$ is this number. This algorithm
depends on a collection of integers $B_{1},\ldots,B_{k}$, $P^{*},c,\delta$
and $n_{0}$. $n_{0}$ is the number of samples to use in the first
stage of samples, and $100$ is the recommended value for $n_{0}$.
$B_{x}$ controls the number of samples taken from system $x$ in
each stage.

@@

@@

\vspace{10mm}
This algorithm generalizes the BIZ procedure with known common variance. In that case, we have that$B_1=\cdots=B_k=1$ and $n_{tx}=t$. The algorithm 2 can be generalized to the continuous case (See appendix B and Frazier (2014)). This procedure is a slightly modification of the original BIZ procedure where $z \in \mbox{arg max}_{x\in A} \lambdahat^2_{tx}$, instead of $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambdahat^2_{tx}$.

\section{Asymptotic Validity when the Variances are Known}

In this section we prove that the BIZ procedure satisfies the IZ guarantee
when the variances are known and $\delta\rightarrow0$, where the
vector of the true means $\mu=\left[\mu_{k},\ldots,\mu_{1}\right]$
is equal to $\delta a$ for some $a\in\mathbb{R}^{k}$ and $\delta>0$.
Without loss of generality suppose that the true means satisfy that
$\mu_{k}>\mu_{k-1}\geq\cdots\geq\mu_{1}$. We suppose that samples
from system $x\in\left\{ 1\ldots,k\right\} $ are identically distributed
and independent, over time and across alternatives. We also define
$\lambda_{z}^{2}:=\max_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}$
and we suppose that $\mbox{min}{}_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}>0$
and $\mbox{max}{}_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}<\infty$.

@@

First, we are going to see that the the standardized sum of the output
data converges to a Brownian motion in the sense of $D_{\infty}:=D[0,\infty)$,
which is the set of functions from $\left[0,\infty\right)$ to $\mathbb{R}$
that are right-continuous and have left-hand limits, with the Skorohod
topology. The definition and the properties of this topology may be
found in Chapter 3 of Billingsley 1999 and the appendix.

@@

The following lemma shows that the standardized sum of the output
data with $t$ changed by $t/\delta^{2}$ converges to a Brownian
motion in the sense of $D_{\infty}$.

\paragraph*{Lemma 1.}

For each $x\in\left\{ 1\ldots,k\right\} $, we define
\[
\mathcal{C}_{x}\left(\delta,t\right)=\frac{Y_{n_{x}\left(t\right),x}-t\lambda_{x}^{2}\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}\delta}}
\]
where $Y_{n,x}$ is the sum of the first $n$ samples from alternative
$x$. Let $x\in\left\{ 1\ldots,k\right\} $, then
\[
\mathcal{C}_{x}\left(\delta,\cdot\right)\Rightarrow W_{x}\left(\cdot\right)
\]
as $\delta\rightarrow0$ in the sense of $D[0,\infty)$, where $W_{x}$
is a standard Brownian motion.

\paragraph*{Proof.}

By Theorem 19.1 of Billingsley 1999,

@@

$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$

${\color{white}sssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssss}$$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$

Now, we use the product topology in $D^{k}\left[0,\infty\right)$
for $k\in\mathbb{N}$. This topology may be described as the one under
which $\left(Z_{n}^{1},\ldots,Z_{n}^{k}\right)\rightarrow\left(Z_{0}^{1},\ldots,Z_{0}^{k}\right)$
if and only if $Z_{n}^{i}\rightarrow Z_{0}^{i}$ for all $i\in\left\{ 1,\ldots,k\right\} $.
See the Miscellany of Billingsley 1968. The following corollary follows
from the previous result and independence.

\paragraph*{Corollary 1.}

We have that
\[
\mathcal{C}\left(\delta,\cdot\right):=\left(\mathcal{C}_{x}\left(\delta,\cdot\right)\right)_{x\in A}\Rightarrow W\left(\cdot\right):=\left(W_{x}\left(\cdot\right)\right)_{x\in A}
\]
as $\delta\rightarrow0$ in the sense of $D_{\infty}^{k}$.\\

@@

In order to prove this, we first prove a continuity property in Lemma
2, which will allow us to use Theorem 5.5 of Billingsley 1968, which
implies the desired result.

\paragraph*{Lemma 2.}

Let $\left\{ \delta_{n}\right\} \subset\left(0,\infty\right)$ such
that $\delta_{n}\rightarrow0$. If $D_{s}\equiv\{Z\in D\left[0,\infty\right)^{k}:\mbox{ if }\left\{ Z_{n}\right\} \subset D\left[0,\infty\right)^{k}\mbox{ and }$
$\mbox{lim}{}_{n}d_{\infty}\left(Z_{n},Z\right)=0$ , then the sequence
$\left\{ f\left(Z_{n},\delta_{n}\right)\right\} $ converges to $\left\{ g\left(Z\right)\right\} $$\left.\right\} $$ $,
then $ $$\mathbb{P}\left(W\text{\ensuremath{\in}}D_{s}\right)=1$.\\

First, we are going to prove the following five results.\\

\paragraph*{Proposition 1.}

Suppose $\left\{ f_{n}\right\} $ and $\left\{ g_{n}\right\} $ are
two sequences of functions on $D_{\infty}$ such that $f_{n}\rightarrow f$
and $g_{n}\rightarrow g$ in $D_{\infty}$. If $f$ and $g$ are continuous,
then
\[
\mbox{min}\left(f_{n},g_{n}\right)\rightarrow\mbox{min}\left(f,g\right)
\]
in $D_{\infty}$.

\paragraph*{Proof.}

Let $t^{*}>0$. We will prove that $\mbox{min}\left(f_{n},g_{n}\right)\rightarrow\mbox{min}\left(f,g\right)$
in $D_{t^{*}}$ and the theorem will follow from Theorem 16.2 of Billingsley
1999.

Since $f$ and $g$ are uniformly continuous in $\left[0,t^{*}\right]$
and $f_{n}\rightarrow f$ and $g_{n}\rightarrow g$ in $\left[0,t^{*}\right]$,
then $ $ $f_{n}$ and $g_{n}$ converge uniformly to $f$ and $g$,
respectively. Consequently, $\left(f_{n},g_{n}\right)\rightarrow\left(f,g\right)$
uniformly in $\left[0,t^{*}\right]$. Let $a_{f}^{+}=\mbox{max}_{t\in\left[0,t^{*}\right]}\left|f(t)\right|$,
$a_{f}^{-}=-a_{f}^{+}$, $a_{g}^{+}=\mbox{max}_{t\in\left[0,t^{*}\right]}\left|g(t)\right|$
and $a_{g}^{-}=-a_{g}^{+}$. Let $N$ such that if $n\geq N$, implies
$\left|f_{n}\left(t\right)-f\left(t\right)\right|<1$ and $\left|g_{n}\left(t\right)-g\left(t\right)\right|<1$
for all $t\in\left[0,t^{*}\right]$. Consequently, if $n\geq N$,$ $
$f_{n}\left(t\right)\in\left[a_{f}^{-}-1,a_{f}^{+}+1\right]$ and
$g_{n}\left(t\right)\in\left[a_{g}^{-}-1,a_{g}^{+}+1\right]$ for
all $t$ in $\left[0,t^{*}\right]$. Since $\mbox{min}\left(x,y\right)$
is continuous, then it is uniformly continuous in $A=\left[a_{f}^{-}-1,a_{f}^{+}+1\right]\times\left[a_{g}^{-}-1,a_{g}^{+}+1\right]$.

>>>>

%**************************************************************************
%*
%*  Paper: ``INSTRUCTIONS FOR AUTHORS OF LATEX DOCUMENTS''
%*
%*  Publication: 2015 Winter Simulation Conference Author Kit
%*
%*  Filename: wsc15paper.tex
%*
%*  Date: January 31, 2001   Time:  9:45 PM
%*      BASE of current version: Feb 01, 2010 (primary WSC'10 LaTeX file)
%*
%*  Word Processing System: TeXnicCenter and MiKTeX
%*
%*
%*  All files need the following
\input{wsc15style.tex}     % download from author kit.  Style files for wsc formatting. Don't remove this line - required for generating the final paper!

\documentclass{wscpaperproc}
\usepackage{latexsym}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{mathptmx}

%
%****************************************************************************
% AUTHOR: You may want to use some of these packages. (Optional)
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algorithmic}
%****************************************************************************

%
%****************************************************************************
% AUTHOR: If you do not wish to use hyperlinks, then just comment
% out the hyperref usepackage commands below.

%% This version of the command is used if you use pdflatex. In this case you
%% cannot use ps or eps files for graphics, but pdf, jpeg, png etc are fine.

\usepackage[pdftex,colorlinks=true,urlcolor=blue,citecolor=black,anchorcolor=black,linkcolor=black]{hyperref}

%% The next versions of the hyperref command are used if you adopt the
%% outdated latex-dvips-ps2pdf route in generating your pdf file. In
%% this case you can use ps or eps files for graphics, but not pdf, jpeg, png etc.
%% However, the final pdf file should embed all fonts required which means that you have to use file
%% formats which can embed fonts. Please note that the final PDF file will not be generated on your computer!
%% If you are using WinEdt or PCTeX, then use the following. If you are using
%% Y&Y TeX then replace "dvips" with "dvipsone"

%%\usepackage[dvips,colorlinks=true,urlcolor=blue,citecolor=black,%
%% anchorcolor=black,linkcolor=black]{hyperref}
%****************************************************************************

%
%****************************************************************************
%*
%* AUTHOR: YOUR CALL!  Document-specific macros can come here.
%*
%****************************************************************************

@@

% If you use theoremes
\newtheoremstyle{wsc}% hnamei
{3pt}% hSpace abovei
{3pt}% hSpace belowi
{}% hBody fonti
{}% hIndent amounti1
{\bf}% hTheorem head fontbf
{}% hPunctuation after theorem headi
{.5em}% hSpace after theorem headi2
{}% hTheorem head spec (can be left empty, meaning `normal')i

\theoremstyle{wsc}
\newtheorem{theorem}{Theorem}
\renewcommand{\thetheorem}{ \arabic{theorem}}
\newtheorem{corollary}{Corollary}
\renewcommand{\thecorollary}{\arabic{corollary}}
\newtheorem{definition}{Definition}
\renewcommand{\thedefinition}{\arabic{definition}}
\newtheorem{lemma}{Lemma}
\renewcommand{\thelemma}{\arabic{lemma}}

%#########################################################
%*
%*  The Document.
%*
\begin{document}

%***************************************************************************
% AUTHOR: AUTHOR NAMES GO HERE
% FORMAT AUTHORS NAMES Like: Author1, Author2 and Author3 (last names)
%
%		You need to change the author listing below!
%               Please list ALL authors using last name only, separate by a comma except
%               for the last author, separate with "and"
%
\WSCpagesetup{Toscano-Palmerin, Frazier}

% AUTHOR: Enter the title, all letters in upper case
\title{ASYMPTOTIC VALIDITY OF A FULLY SEQUENTIAL ELIMINATION PROCEDURE FOR INDIFFERENCE-ZONE RANKING AND SELECTION WITH TIGHT BOUNDS ON PROBABILITY OF CORRECT SELECTION}

\maketitle

\begin{figure*}[htb]
{
\centering
Saul Toscano-Palmerin \\
Peter I. Frazier \\
\vspace{12pt}
Cornell University \\
257 Rhodes Hall \\
206 Rhodes Hall \\
Ithaca, NY 14853, USA\\
}
\end{figure*}

\section*{ABSTRACT}
We consider the indifference-zone (IZ) formulation of the ranking
and selection problem in which the goal is to choose with high probability 
an alternative with similar mean than the one with largest mean. 
Conservatism leads classical IZ procedures
to take too many samples in problems with many alternatives. The Bayes-inspired
Indifference Zone (BIZ) procedure, proposed in \citeN{Frazier:BIZ}, is
less conservative than previous procedures, but its proof of validity
requires strong assumptions, specifically it assumes that the variances are known 
and have an integer multiple structure. In this paper, we consider a slightly
modification of the original BIZ procedure in order to simplify the analysis, and we
present a new proof of its asymptotic validity that relaxes these assumptions.
Specifically, we prove the validity of the algorithm when the variances are known
and the difference between the best alternative and the second best goes to zero.

\section{INTRODUCTION}
\label{sec:intro}

There are many applications where we have to choose the best alternative
among a finite number of simulated alternatives. For example, in inventory problems, we may want to choose the best inventory policy $(s,S)$ for a finite number of values of $s$ and $S$. The ranking and selection problem has to decide how many samples are needed to find the alternative with the largest mean. A good solution to the problem is efficient and accurate, i.e. the procedure proposed for the problem must balance between the number of samples required and quality of the selection.

This paper considers the indifference-zone (IZ) formulation of
the ranking and selection problem, in which the distance between the best system and
the other systems is sufficiently large and the best system is chosen with probability larger
than some threshold given by the user. This property is called the IZ guarantee, and the preference zone (PZ)
is defined as the set of system configurations under which the difference between the best system and the others is
at least some given  $\delta>0$. The paper \citeN{Bechhofer:1954} is considered the seminal work, and early work is 
presented in the monograph \citeN{Bechhofer:1968}. Some compilations of the theory developed in the area can be found
in \citeN{Bechhofer:1995}, \citeN{swisher:survey}, \citeN{kim:20062} and \citeN{kim:2007}. Beyond these classical approaches, 
there are the Bayesian approach \cite{Frazier:Tutorial} and the optimal computing budget allocation approach \cite{chen:ocva}.

A good IZ procedure satisfies the IZ guarantee and requires as few samples as possible.
The first IZ procedures presented in \citeN{Bechhofer:1954}, \citeN{Paulson:01}, \citeN{Fabian}, \citeN{Rinott},
\citeN{Harmann:1988}, \citeN{hartmann:sequential}, \citeN{Paulson:1994} 
satisfy the IZ guarantee, but they usually take too many samples when there are many alternatives,
in part because their probability of correct selection (PCS) is much
larger than the probability specified by the user \cite{kim:Conserv}. One reason for this
is that these procedures use Bonferroni's inequality, which leads then to sample more
than necessary. More recently, new algorithms were developed in \citeN{Kim:2001}, \citeN{Goldsman:2002}, 
\citeN{Hong}, and they improve the performance but they still
use the Bonferroni's inequality, and so the methods are inefficient
when there are many alternatives. Procedures in \citeN{kim:2011},
\citeN{dieker:2012} do not use the Bonferroni's inequality 
when there are only three alternatives, but when they compare more than three
alternatives, they do use the Bonferroni's inequality.

Conservative algorithms lead to take more samples than needed, and consequently conservative procedures are unpopular 
when there are more than a few hundred of alternatives. Three common sources of conservativeness are
 the Bonferroni's inequality, the change from discrete process to continuous process, and bound the worst case which is not a common case.
  \citeN{Frazier:BIZ} eliminates one source of conservativeness: the Bonferroni's inequality. He presented  a new sequential elimination
IZ procedure, called BIZ (Bayes-inspired Indifference Zone), whose
lower bound on worst-case probability of correct selection in the
preference zone is tight in continuous time, and almost tight in the
discrete time. In numerical experiments, the number of samples required
by BIZ is significantly smaller than that of procedures like the KN procedure of \citeN{Kim:2001} and
the $\mathcal{P}_{B}^{*}$ procedure of \citeN{Bechhofer:1968}, 
especially on problems with many alternatives. Unfortunately, the
proof that the BIZ procedure satisfies the IZ guarantee for the discrete-time
case assumes that variances are known and have an integer multiple
structure which is not very realistic.

The contribution of this work is that we prove the asymptotic validity of the 
BIZ procedure for the discrete-time case when the variances are known and $\delta$ goes to zero. 
In order to simplify analysis, we consider a slightly modification of this procedure.
Although we only proved it in the known variance setting, it is still a significantly
generalization over the assumption that the variances are known and have an integer multiple
structure. Furthermore, we do not need to assume that the alternatives follow a normal distribution. 
The only assumptios are that the alternatives are independent, identically distributed and have
finite variance. We conjecture that these techniques can be used to show the validity of this procedure when
the variances are unknown, and we present numerical experiments that support this belief. 
\citeN{kim:asympt} also proves the asymptotical validity of a IZ procedure in the same limit.
Our proof shares some similarities since we both use a central limit theorem.

This paper is organized as follows: In $\text{ß}2$, we recall the
indifference-zone ranking and selection problem. In $\text{ß}3$,
we recall the Bayes-inspired IZ (BIZ) procedure from \citeN{Frazier:BIZ}. In $\text{ß}4$,
we present the proof of the validity of the algorithm when the variances
are known. In $\text{ß}5$, we present some numerical experiments. 
In $\text{ß}6$, we conclude.

\section{INDIFFERENCE-ZONE RANKING AND SELECTION}

Ranking and Selection is a problem where we have to select the best system
among a finite set of alternatives, i.e. the system with the largest
mean. The method selects a system as the best based on the samples
that are observed sequentially over time. We suppose that samples
are identically distributed and independent, over time and across alternatives, and
each alernative $x$ has mean $\mu_{x}$. We define $\mu=(\mu_{1},\ldots,\mu_{k})$.

If the best system is selected, we say that the procedure has made the \emph{correct selection}
(CS). We define the \emph{probability of correct selection} as 
\[
\mbox{PCS}\left(\mu\right)=\mathbb{P}_{\mu}\left(\hat{x}\in\mbox{arg max}_{x}\mu_{x}\right)
\]
where $\hat{x}$ is the alternative chosen by the procedure and $\mathbb{P}_{\mu}$
is the probability measure under which samples from system $x$ have
mean $\mu_{x}$ and finite variance $\lambda_{x}^{2}$.

In the Indifference-Zone Ranking and Selection, the procedure is indifferent
in the selection of a system whenever the means of the populations
are nearly the same. Formally, let $\mu=\left[\mu_{k},\ldots,\mu_{1}\right]$
be the vector of the true means, the \emph{indifference zone} is defined
as the set $\left\{ \mu\in\mathbb{R}^{k}:\mu_{\left[k\right]}-\mu_{\left[k-1\right]}<\delta\right\} $.
The complement of the indifference zone is called the \emph{preference
zone} (PZ) and $\delta>0$ is called the indifference zone parameter.
We say that a procedure meets the \emph{indifference-zone (IZ) guarantee
}at $P^{*}\in\left(1/k,1\right)$ and $\delta>0$ if
\[
\mbox{PCS}\left(\mu\right)\geq P^{*}\mbox{ for all }\mu\in\mbox{PZ}\left(\delta\right).
\]
We assume $P^{*}>1/k$ because IZ guarantees can be meet by choosing
$\hat{x}$ uniformly at random from among $\left\{ 1,\ldots,k\right\} $.

\section{THE BAYES-INSPIRED IZ (BIZ) PROCEDURE}

BIZ is an elimination procedure. This procedure maintains a set of
alternatives that are candidates for the best system, and it takes samples from each
alternative in this set at each point in time. At beginning, all alternatives
are possible candidates for the best system, and over the time alternatives are eliminated.
The procedure ends when there is only one alternative in the contention
set and this remain alternative is chosen as the best.

Frazier \cite{Frazier:BIZ} showed that the BIZ procedure with known common variance
satisfies the IZ guarantee when the systems follow the normal distribution
, with tight bounds on worst-case preference-zone in continuous time.
He also proved that this procedure retains the IZ guarantee when the
systems follow the normal distribution, and the variances are known
and are integer multiples of a common value. The continuous time version
of this procedure also satisfies the IZ guarantee, with a tight worst-case
preference-zone PCS bound.

The discrete-time BIZ procedure for unknown and/or heterogeneous sampling
variances is given below.  It takes a variable number of samples
from each alternative, and $n_{tx}$ is this number. This algorithm
depends on a collection of integers $B_{1},\ldots,B_{k}$, $P^{*},c,\delta$
and $n_{0}$. $n_{0}$ is the number of samples to use in the first
stage of samples, and $100$ is the recommended value for $n_{0}$.
$B_{x}$ controls the number of samples taken from system $x$ in
each stage. The procedure presented is a slightly modification of the original BIZ 
procedure where $z \in \mbox{arg max}_{x\in A} \lambdahat^2_{tx}$, instead 
of $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambdahat^2_{tx}$.

@@

\vspace{5mm}

@@

\vspace{10mm}
This algorithm generalizes the BIZ procedure with known common variance. In that case, we have that$B_1=\cdots=B_k=1$ and $n_{tx}=t$. The algorithm 2 can be generalized to the continuous case (See  \citeN{Frazier:BIZ}).

\section{ASYMPTOTIC VALIDITY WHEN THE VARIANCES ARE KNOWN}

In this section we prove that the BIZ procedure satisfies asymptotically the IZ guarantee
when the variances are known. This means that we consider a collection of
ranking and selection problems parametrized by $\delta>0$.  
For the problem given $\delta$, we suppose that the vector of the true means
$\mu=\left[\mu_{k},\ldots,\mu_{1}\right]$ is equal to $\delta a$ for some fixed $a\in\mathbb{R}^{k}$ that
does not depend on $\delta$ and $a_{k}>a_{k-1}\geq \cdots \geq a_{1}$, $a_{k}-a_{k-1}>1$.
Moreover, the variances of the alternatives are finite, strictly greater than zero and do not depend on $\delta$.
We also suppose that samples from system $x\in\left\{ 1\ldots,k\right\} $ are identically distributed
and independent, over time and across alternatives. We also define
$\lambda_{z}^{2}:=\max_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}$.

@@

First, we are going to see that the the standardized sum of the output
data converges to a Brownian motion in the sense of $D_{\infty}:=D[0,\infty)$,
which is the set of functions from $\left[0,\infty\right)$ to $\mathbb{R}$
that are right-continuous and have left-hand limits, with the Skorohod
topology. The definition and the properties of this topology may be
found in Chapter 3 of \citeN{billingsley:convergnce2}.

@@

The following lemma shows that the standardized sum of the output
data with $t$ changed by $t/\delta^{2}$ converges to a Brownian
motion in the sense of $D_{\infty}$. 
\\
\begin{lemma}
For each $x\in\left\{ 1\ldots,k\right\} $, we define
\[
\mathcal{C}_{x}\left(\delta,t\right)=\frac{Y_{n_{x}\left(t\right),x}-t\lambda_{x}^{2}\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}\delta}}
\]
where $Y_{n,x}$ is the sum of the first $n$ samples from alternative
$x$. Let $x\in\left\{ 1\ldots,k\right\} $, then
\[
\mathcal{C}_{x}\left(\delta,\cdot\right)\Rightarrow W_{x}\left(\cdot\right)
\]
as $\delta\rightarrow0$ in the sense of $D[0,\infty)$, where $W_{x}$
is a standard Brownian motion.

\end{lemma}

\begin{proof}
By Theorem 19.1 of  \citeN{billingsley:convergnce2},

@@

\end{proof}

Now, we use the product topology in $D^{k}\left[0,\infty\right)$
for $k\in\mathbb{N}$. This topology may be described as the one under
which $\left(Z_{n}^{1},\ldots,Z_{n}^{k}\right)\rightarrow\left(Z_{0}^{1},\ldots,Z_{0}^{k}\right)$
if and only if $Z_{n}^{i}\rightarrow Z_{0}^{i}$ for all $i\in\left\{ 1,\ldots,k\right\} $.
See the Miscellany of  \citeN{billingsley:convergence}. The following corollary follows
from the previous result and independence.

\vspace{5mm}

\begin{corollary}
We have that
\[
\mathcal{C}\left(\delta,\cdot\right):=\left(\mathcal{C}_{x}\left(\delta,\cdot\right)\right)_{x\in A}\Rightarrow W\left(\cdot\right):=\left(W_{x}\left(\cdot\right)\right)_{x\in A}
\]
as $\delta\rightarrow0$ in the sense of $D_{\infty}^{k}$.
\end{corollary}

\vspace{5mm}

@@

In order to prove this, we first proved a continuity property in Lemma
2, which allows us to use Theorem 5.5 of \citeN{billingsley:convergence}, which
implies the desired result. A proof of Lemma 2 may be found in a full version which will be
submitted soon to arXiv. 
\\
\begin{lemma}
